Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-09-23 Paper.tex
Add \usepackage{underscore}
To prevent builds failing that have underscores in URLs.
Fee Schedule grammar

\documentclass[9pt,oneside]{amsart}
%\usepackage{tweaklist}
\usepackage{url}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{hyperref}

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description* \\
\midrule
$G_{zero}$ & 0 & Nothing paid for operations of the set {\small $W_{zero}$}. \\
$G_{base}$ & 2 & Amount of gas to pay for operations of the set {\small $W_{base}$}. \\
$G_{verylow}$ & 3 & Amount of gas to pay for operations of the set {\small $W_{verylow}$}. \\
$G_{low}$ & 5 & Amount of gas to pay for operations of the set {\small $W_{low}$}. \\
$G_{mid}$ & 8 & Amount of gas to pay for operations of the set {\small $W_{mid}$}. \\
$G_{high}$ & 10 & Amount of gas to pay for operations of the set {\small $W_{high}$}. \\
$G_{extcode}$ & 700 & Amount of gas to pay for operations of the set {\small $W_{extcode}$}. \\
$G_{balance}$ & 400 & Amount of gas to pay for a {\small BALANCE} operation. \\
$G_{sload}$ & 200 & Paid for a {\small SLOAD} operation. \\
$G_{jumpdest}$ & 1 & Paid for a {\small JUMPDEST} operation. \\
$G_{sset}$ & 20000 & Paid for an {\small SSTORE} operation when the storage value is set to non-zero from zero. \\
$G_{sreset}$ & 5000 & Paid for an {\small SSTORE} operation when the storage value's zeroness remains unchanged or is set to zero. \\
$R_{sclear}$ & 15000 & Refund given (added into refund counter) when the storage value is set to zero from non-zero. \\
$R_{selfdestruct}$ & 24000 & Refund given (added into refund counter) for self-destructing an account. \\
$G_{selfdestruct}$ & 5000 & Amount of gas to pay for a {\small SELFDESTRUCT} operation. \\
$G_{create}$ & 32000 & Paid for a {\small CREATE} operation. \\
$G_{codedeposit}$ & 200 & Paid per byte for a {\small CREATE} operation to succeed in placing code into state. \\
$G_{call}$ & 700 & Paid for a {\small CALL} operation. \\
$G_{callvalue}$ & 9000 & Paid for a non-zero value transfer as part of the {\small CALL} operation. \\
$G_{callstipend}$ & 2300 & A stipend for the called contract subtracted from $G_{callvalue}$ for a non-zero value transfer. \\
$G_{newaccount}$ & 25000 & Paid for a {\small CALL} or {\small SELFDESTRUCT} operation which creates an account. \\
$G_{exp}$ & 10 & Partial payment for an {\small EXP} operation. \\
$G_{expbyte}$ & 50 & Partial payment when multiplied by $\lceil\log_{256}(exponent)\rceil$ for the {\small EXP} operation. \\
$G_{memory}$ & 3 & Paid for every additional word when expanding memory. \\
$G_\text{txcreate}$ & 32000 & Paid by all contract-creating transactions after the {\it Homestead transition}.\\
$G_{txdatazero}$ & 4 & Paid for every zero byte of data or code for a transaction. \\
$G_{txdatanonzero}$ & 68 & Paid for every non-zero byte of data or code for a transaction. \\
$G_{transaction}$ & 21000 & Paid for every transaction. \\
$G_{log}$ & 375 & Partial payment for a {\small LOG} operation. \\
$G_{logdata}$ & 8 & Paid for each byte in a {\small LOG} operation's data. \\
$G_{logtopic}$ & 375 & Paid for each topic of a {\small LOG} operation. \\
$G_{sha3}$ & 30 & Paid for each {\small SHA3} operation. \\
$G_{sha3word}$ & 6 & Paid for each word (rounded up) for input data to a {\small SHA3} operation. \\
$G_{copy}$ & 3 & Partial payment for {\small *COPY} operations, multiplied by words copied, rounded up. \\
$G_{blockhash}$ & 20 & Payment for {\small BLOCKHASH} operation. \\

>>>>

\documentclass[9pt,oneside]{amsart}
%\usepackage{tweaklist}
\usepackage{url}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
\usepackage{hyperref}

@@

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description* \\
\midrule
$G_{zero}$ & 0 & Nothing is paid for operations of the set {\small $W_{zero}$}. \\
$G_{base}$ & 2 & This is the amount of gas to pay for operations of the set {\small $W_{base}$}. \\
$G_{verylow}$ & 3 & This is the amount of gas to pay for operations of the set {\small $W_{verylow}$}. \\
$G_{low}$ & 5 & This is the amount of gas to pay for operations of the set {\small $W_{low}$}. \\
$G_{mid}$ & 8 & This is the amount of gas to pay for operations of the set {\small $W_{mid}$}. \\
$G_{high}$ & 10 & This is the amount of gas to pay for operations of the set {\small $W_{high}$}. \\
$G_{extcode}$ & 700 & This is the amount of gas to pay for operations of the set {\small $W_{extcode}$}. \\
$G_{balance}$ & 400 & This is the amount of gas to pay for a {\small BALANCE} operation. \\
$G_{sload}$ & 200 & This is paid for an {\small SLOAD} operation. \\
$G_{jumpdest}$ & 1 & This is paid for a {\small JUMPDEST} operation. \\
$G_{sset}$ & 20000 & This is paid for an {\small SSTORE} operation when the storage value is set to non-zero from zero. \\
$G_{sreset}$ & 5000 & This is the amount for an {\small SSTORE} operation when the storage value's zeroness remains unchanged or is set to zero. \\
$R_{sclear}$ & 15000 & This is the refund given (added into the refund counter) when the storage value is set to zero from non-zero. \\
$R_{selfdestruct}$ & 24000 & This is the refund given (added into the refund counter) for self-destructing an account. \\
$G_{selfdestruct}$ & 5000 & This is the amount of gas to pay for a {\small SELFDESTRUCT} operation. \\
$G_{create}$ & 32000 & This is paid for a {\small CREATE} operation. \\
$G_{codedeposit}$ & 200 & This is paid per byte for a {\small CREATE} operation to succeed in placing code into the state. \\
$G_{call}$ & 700 & This is paid for a {\small CALL} operation. \\
$G_{callvalue}$ & 9000 & This is paid for a non-zero value transfer as part of the {\small CALL} operation. \\
$G_{callstipend}$ & 2300 & This is a stipend for the called contract subtracted from $G_{callvalue}$ for a non-zero value transfer. \\
$G_{newaccount}$ & 25000 & This is paid for a {\small CALL} or for a {\small SELFDESTRUCT} operation which creates an account. \\
$G_{exp}$ & 10 & This is a partial payment for an {\small EXP} operation. \\
$G_{expbyte}$ & 50 & This is a partial payment when multiplied by $\lceil\log_{256}(exponent)\rceil$ for the {\small EXP} operation. \\
$G_{memory}$ & 3 & This is paid for every additional word when expanding memory. \\
$G_\text{txcreate}$ & 32000 & This is paid by all contract-creating transactions after the {\it Homestead transition}.\\
$G_{txdatazero}$ & 4 & This is paid for every zero byte of data or code for a transaction. \\
$G_{txdatanonzero}$ & 68 & This is paid for every non-zero byte of data or code for a transaction. \\
$G_{transaction}$ & 21000 & This is paid for every transaction. \\
$G_{log}$ & 375 & This is a partial payment for a {\small LOG} operation. \\
$G_{logdata}$ & 8 & This is paid for each byte in a {\small LOG} operation's data. \\
$G_{logtopic}$ & 375 & This is paid for each topic of a {\small LOG} operation. \\
$G_{sha3}$ & 30 & This is paid for each {\small SHA3} operation. \\
$G_{sha3word}$ & 6 & This is paid for each word (rounded up) for input data to a {\small SHA3} operation. \\
$G_{copy}$ & 3 & This is a partial payment for {\small *COPY} operations, multiplied by the number of words copied, rounded up. \\
$G_{blockhash}$ & 20 & This is a payment for a {\small BLOCKHASH} operation. \\
